Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/motivation.tex
Motivation

Implementations of the X.509 format for SSL certificates were also shown to parse various ASN.1
structures, such as length fields, strings containing invalid characters and repeated fields with
conflicting values different~\cite{DBLP:conf/fc/KaminskyPS10}. For example, certificates could be
crafted where the X.509 parsers used certificate authorities and web browsers disagree on the
subject of the certificate, allowing an attacker to get certificates for domains they do not control.

>>>>

Similarly, vulnerabilities in X.509 parsers for SSL certificates allowed attackers to get
certificates for domains they do not control. First, Moxie Marlinspike discovered that the X.509
parsers in popular browsers handle NUL-bytes in certificates incorrectly~\cite{Marlinspike:SSL}. After this
vulnerability was fixed, Dan Kaminsky discovered~\cite{DBLP:conf/fc/KaminskyPS10} that other
structures, such as length fields and duplicated data, were also handled incorrectly.
